The connection between star formation rate and dark matter halo mass during reionization

### 2015-09-03 paper/ms.tex
Chi2 plots
Bouwens

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $18.07_{-0.06}^{+0.10}$ & 0.03 & $17.81_{-0.08}^{+0.12}$ & 0.02  \\
$\log_{10}(M_0/M_{\odot})$ & $11.19_{-0.03}^{+0.67}$ & 0.07 & $11.12_{-0.24}^{+0.58}$ & 0.06  \\
$\beta$                    & $1.480_{-1.28}^{+0.11}$ & 0.18 & $ 1.44_{-1.35}^{+0.16}$ & 0.18  \\
$\gamma\times0.1$          & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.46  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the Willott data with and without 
dust attenuation over 64 small boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:Willott_best_fit_parameters_no_dust}
\end{center}
\end{table}

\begin{figure}
\epsscale{1.00}
\plotone{fig/OD1_chi2_comparison.pdf}
\caption{Best fit to Willott comparison between the two models. Each point represent $\chi^2$ 
calculated over each small-box. The solid line represents the ratio 1:1 }
\label{fig:OD1_chi2_comparison}
\end{figure}

>>>>

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $18.07_{-0.06}^{+0.10}$ & 0.03 & $17.81_{-0.08}^{+0.12}$ & 0.02  \\
$\log_{10}(M_0/M_{\odot})$ & $11.19_{-0.03}^{+0.67}$ & 0.07 & $11.12_{-0.24}^{+0.58}$ & 0.06  \\
$\beta$                    & $1.480_{-1.28}^{+0.11}$ & 0.18 & $ 1.44_{-1.35}^{+0.16}$ & 0.18  \\
$\gamma\times0.1$          & $4.028_{-0.82}^{+3.01}$ & 0.58 & $ 5.18_{-0.59}^{+2.36}$ & 0.58  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the Willott data with and without 
dust attenuation over 64 small boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:Willott_best_fit_parameters_no_dust}
\end{center}
\end{table}

\begin{table}
\begin{center}
\begin{tabular}{cccccc}\hline\hline
 & \multicolumn{2}{c}{Dust Att.} & \multicolumn{2}{c}{No-Dust Att.}\\
Parameter                  & MCMC                  & C.Var. & MCMC                    & C.Var. \\\hline
$\log_{10}(L_0/L_{\odot})$ & $18.27_{-0.22}^{+0.33}$ & 0.03 & $17.81_{-0.16}^{+0.22}$ & 0.06  \\
$\log_{10}(M_0/M_{\odot})$ & $11.43_{-0.49}^{+0.57}$ & 0.07 & $11.82_{-0.32}^{+1.02}$ & 0.13  \\
$\beta$                    & $ 0.88_{-0.27}^{+0.39}$ & 0.18 & $ 0.91_{-0.48}^{+0.63}$ & 0.04  \\
$\gamma\times0.1$          & $ 1.41_{-1.41}^{+7.58}$ & 0.58 & $ 1.34_{-1.34}^{+6.77}$ & 0.13  \\
\hline\hline
\end{tabular}
\caption{ Best fit parameters to the Bouwens data with and without 
dust attenuation over 8 tiny boxes. Mean best value estimated 
with MCMC, mean $1\sigma$ confidence interval and Cosmic Variance
(C.Var.)
} 
\label{table:Bouwens_best_fit_parameters_no_dust}
\end{center}
\end{table}

\begin{figure}
\epsscale{1.00}
\plotone{fig/chi2_OD1.pdf}
\caption{Best fit to Willott comparison between the two models. Each point represent $\chi^2$ 
calculated over each small-box. The solid line represents the ratio 1:1 }
\label{fig:OD1_chi2_comparison}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/chi2_OD2.pdf}
\caption{Best fit to Bouwens between the two models. Each point represent $\chi^2$ 
calculated over each small-box. The solid line represents the ratio 1:1 }
\label{fig:OD2_chi2_comparison}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/chi2_OD3.pdf}
\caption{Best fit to McLure comparison between the two models. Each point represent $\chi^2$ 
calculated over each small-box. The solid line represents the ratio 1:1 }
\label{fig:OD3_chi2_comparison}
\end{figure}

\begin{figure}
\epsscale{1.00}
\plotone{fig/chi2_OD4.pdf}
\caption{Best fit to Finkelstein comparison between the two models. Each point represent $\chi^2$ 
calculated over each small-box. The solid line represents the ratio 1:1 }
\label{fig:OD4_chi2_comparison}
\end{figure}
